---
title: "Learn tokencodr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Learn tokencodr }
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

This package was inspired by [gargle](https://gargle.r-lib.org). Indeed, much of the code in this package is adapted directly from the `secret_*` family of functions used by gargle internally. The methods employed here are directly adapted from this [vignette on securely managing tokens](https://gargle.r-lib.org/articles/articles/managing-tokens-securely.html). I hope `tokencodr` will make it easy for people to encrypt authentication tokens for both interactive and non-interactive usage. 

> **DISCLAIMER:** I am not a security expert. The methods described in this package could potentially allow certain parties to access your authorization token(s) and, subsequently, your data. Use at your own risk.

As an overview, I will describe how to use this package in-tandem with [boxr](https://r-box.github.io/boxr/index.html), a 'lightweight, *opinionated*, high-level R interface to the box.com API.'

The first step would be to create an environmental variable using the `create_env_pw()` function. This accepts a 'service' argument, which would typically be a one-word description for the platform whose token you are attempting to encrypt. 

In this case, we are looking to encrypt a Box.com token, so I will call `create_env_pw("BOXR")`. This will generate an environmental variable that can be added to the '.Renviron'. file for safe-keeping.

Tokens, like those used in arcade games, can be thought of as a coin. One side stores a username and the other a password. Multiple tokens, with different permissions, can provide access to a given account. They can be easily shared (e.g. as a JSON file) and allow access to applications, such as Google Drive, without requiring a person manually login.

Following the [boxr](https://r-box.github.io/boxr/articles/boxr-app-service.html) documentation, I can generate a JSON web token (JWT), which contains login credentials for a service application -- an app that acts on behalf of the system itself, often with limited scopes. 

To encrypt this, I would simply call `encrypt_token()`. This function accepts the service ("BOXR" in our case), an input file, and the destination directory for where the file should be stored. 

In our case, I may call the following:

```{r, eval = FALSE}
encrypt_token(service = "BOXR", 
              input = "~/private/local/path/to/my/jwt/file.json", 
              destination = "~/Desktop/")
```

If it does not already exist, this will create a ".secret" folder on the Desktop, which is -- on Macs -- a hidden directory. Within that folder, there will be an encrypted file with the name "BOXR" and no extension. Congratulations, you have encrypted your authentication token!

If you are using version control software, such as GitHub, this file can be committed and pushed (assuming it's within a project -- you probably don't want to commit your Desktop files).

In order to use this encrypted token later on, you can simply call `decrypt_token()`, which accepts the service name, path to encrypted token file, and a logical 'complete', indicating whether the file should be returned as raw bytes or as a character string with the decoded (original) contents. 

To use the encrypted token with the boxr package, I would use the `box_auth_service()` function to authenticate the service account token. It accepts either a path specifying a token file, such as the un-encoded one ("~/private/local/path/to/my/jwt/file.json"), or 'token_text', a character vector of the JWT. This is what we will use:

```{r, eval = FALSE}

boxr::box_auth_service(token_text = 
                         decrypt_token(service = "BOXR",
                                       path = "~/Desktop/.secret/BOXR", 
                                       complete = TRUE)
                       )
```

And that's it! Note that I've set `complete = TRUE` to ensure the decoded file is returned, and the path is now pointing to the .secret directory on my Desktop.
